Isomorphisms between algebraic datatypes

### 2025-06-01 QADT/notes.tex
maintenance commit

Everything reduces to the second case, so we analyze that.
\begin{itemize}
  \item If $P(x)=0$, it's trivially true.
  \item If $P(x) = k$, then $X = X + k$, $X \cdot P(X) + X = X (1 + k)$
\end{itemize}
\end{document}

>>>>

Everything reduces to the second case, so we analyze that.
\begin{itemize}
  \item If $P(x)=0$, it's trivially true.
  \item If $P(x) = k$, then $X = X + k$, $X \cdot P(X) + X = X (1 + k)$
\end{itemize}

\section{2025.03.13}

In many cases, some $\mu$ datatype, $\mu F$ being a fixed point of a functor $G$ will not result in a fold isomorphism. \\ 
\textbf{Conjecture: } For all of these situations resulting from a rig isomorphism, all elements of $\mu F$ not in the range of the fold will have an image in the final coalgebra of $G$ which is rational.

We want to try to prove surjectivity of the fold by proving that all preimages of elements of $\mu F$ are well-founded.

\end{document}
